\documentclass[11pt]{article} 
\input{preamble_common.in}
\begin{document}
\begin{recipe}[FrenchOnionSoup]{French Onion Soup}{4 portions}{1 hour}
    \freeform It's just french onion soup.
    \ingredient[1\fr12]{L}{reduced-salt beef or chicken stock}
    Create and heat up vegetable stock until boiling. Remove from heat and set aside. We can use stock cubes as a substitute.
    \ingredient[1]{kg}{onions, thinly sliced}
    \ingredient[2]{pinch}{salt}
    \ingredient[100]{g}{butter}
    Melt butter into a medium high heat pot. Add onions and a few pinches of salt to help with removing moisture. Stir every 5-10 minutes until onions caramelise.
    \ingredient[\fr12]{cup}{dry white wine}
    \ingredient[2]{tbsp}{plain flour}
    When onions are browned, add white wine to deglaze pan. Add the plain flour and stir until incorporated.
    \ingredient[3]{sprigs}{thyme}
    \ingredient[3]{}{bay leaves}
    Add the beef or chicken stock and herbs to the onions. Simmer for 30 minutes.
    \ingredient[1]{loaf}{bread}
    \ingredient[50]{g}{butter}
    \ingredient[3]{cloves}{garlic, minced}
    \ingredient[2]{tsp}{oregano, finely chopped}
    Mix butter, garlic, and oregano to make a garlic butter. Spread garlic butter on bread and toast in oven or grill until almost brown.
    \ingredient[50]{g}{mozerella or cheddar}
    Add cheese liberally onto garlic bread in oven or grill until cheese is melted. Try to avoid browning the cheese.
    \newstep
    Serve bowl of soup with bread on the side.
    \freeform\hrulefill
\end{recipe}
\end{document}